---
title: "Titanic Visualization"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(DT)
library(ggplot2)

titanic = read.csv("E:/Extra/GGPLOT2/titanic.csv",stringsAsFactors = F)

titanic$Pclass <- as.factor(titanic$Pclass)
titanic$Survived <- as.factor(titanic$Survived)
titanic$Sex <- as.factor(titanic$Sex)
titanic$Embarked <- as.factor(titanic$Embarked)
```

Survuval {data-navmenu="Parameters"}
============================================================

Row 
-----------------------------------------------------------------------

### Total Survival Rate

```{r}
ggplot(titanic, aes(x = Survived)) + 
  theme_bw() +
  geom_bar(width = 0.5) +
  labs(y = "Passenger Count",
title = "Titanic Survival Rates")

```



### With respect to sex

```{r}
ggplot(titanic, aes(x = Sex, fill = Survived)) + 
  theme_bw() +
  geom_bar(width = 0.5) +
  labs(y = "Passenger Count",
title = "Titanic Survival Rates by Sex") + scale_fill_manual(name = "Survived",values = c("0" = "red","1" = "limegreen"))
```


Row 
-----------------------------------------------------------------------
### With Respect to Class

```{r}
ggplot(titanic, aes(x = Pclass, fill = Survived)) + 
  theme_bw() +
  geom_bar(width = 0.5) +
  labs(y = "Passenger Count",
title = "Titanic Survival Rates by Pclass")+ scale_fill_manual(name = "Survived",values = c("0" = "red","1" = "limegreen"))
```

### With Respect to Class and Sex

```{r}
ggplot(titanic, aes(x = Sex, fill = Survived)) + 
  theme_bw() +
  facet_wrap(~ Pclass) +
  geom_bar(width = 0.5) +
  labs(y = "Passenger Count",
title = "Titanic Survival Rates by Pclass and Sex")+ scale_fill_manual(name = "Survived",values = c("0" = "red","1" = "limegreen"))
```




Distibution {data-navmenu="Parameters"}
=============================

Column {.tabset}
-----------------------------

### With Respect to Age(Histogram)
```{r}
ggplot(titanic, aes(x = Age)) +
  theme_bw() +
  geom_histogram(binwidth = 5) +
  labs(y = "Passenger Count",
       x = "Age (binwidth = 5)",
title = "Titanic Age Distribtion")
```


### With Respect to Age and Survival(Histogram)

```{r}
ggplot(titanic, aes(x = Age, fill = Survived)) +
  theme_bw() +
  geom_histogram(binwidth = 5) +
  labs(y = "Passenger Count",
       x = "Age (binwidth = 5)",
title = "Titanic Survival Rates by Age")+ scale_fill_manual(name = "Survived",values = c("0" = "red","1" = "limegreen"))
```

### With Respect to Age and Survival(Boxplot)

```{r}
ggplot(titanic, aes(x = Survived, y = Age)) +
  theme_bw() +
  geom_boxplot() +
  labs(y = "Age",
       x = "Survived",
title = "Titanic Survival Rates by Age")
```

Survival with many Parameters  {data-navmenu="Parameters"}
===================================

Column {.tabset}
-----------------------------
### Survival Density With Respect to Age,Sex and Class 

```{r}
ggplot(titanic, aes(x = Age, fill = Survived)) +
  theme_bw() +
  facet_wrap(Sex ~ Pclass) +
  geom_density(alpha = 0.5) +
  labs(y = "Age",
       x = "Survived",
       title = "Titanic Survival Rates by Age, Pclass and Sex")+ scale_fill_manual(name = "Survived",values = c("0" = "red","1" = "limegreen"))
```

### Survival Distribution With Respect to Age,Sex and Class 

```{r}
ggplot(titanic, aes(x = Age, fill = Survived)) +
  theme_bw() +
  facet_wrap(Sex ~ Pclass) +
  geom_histogram(binwidth = 5) +
  labs(y = "Age",
       x = "Survived",
title = "Titanic Survival Rates by Age, Pclass and Sex")+ scale_fill_manual(name = "Survived",values = c("0" = "red","1" = "limegreen"))
```

Survival Percentage {data-navmenu="Parameters" data-orientation=rows}
==============================================================

Row
---------------------------


```{r}

m = titanic %>% filter(Sex == "male") %>% summarise(t_m = n())
f = titanic %>% filter(Sex == "male") %>% summarise(t_m = n())
```

### Male Count
```{r}

valueBox(round(m,2),icon = "fa fa-male",color = 'royalblue')



```




### Female Count
```{r}


valueBox(round(f,2),icon = "fa fa-female",color = 'pink')
```





Row
---------------------------

### Survival Percentage

```{r}
ggplot(titanic,aes(x = 1,y = sort(titanic$Survived),fill = sort(titanic$Survived)))+geom_bar(stat = "identity")+coord_polar(theta = 'y')+theme(panel.background = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(),axis.title.y = element_blank())+labs(y = "Survival ratio")+ scale_fill_manual(name = "Survived",values = c("0" = "red","1" = "limegreen"))
```

Data {data-orientation=rows}
===============================

Row
-----------------------------


###Proportion of not survived

```{r}
p = prop.table(table(titanic$Survived))
p = as.data.frame(p)
```

```{r}

valueBox(round(p[1,2],4),icon = "fa fa-ship",color = "red")
```



###Proportion of survived
```{r}

valueBox(round(p[2,2],4),icon = "fa fa-ship",color = "limegreen")
```



Row
----------------------

### Titanic Data

```{r}

DT::datatable(titanic,options = list(
  bPaginate = T,
  pageLength = 5
))

```

